[DRAFT] - Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data

### 2017-09-21 paper01/paper.tex
Added subsections titles in result section

>>>>

Three different scene configurations were defined in order to test the system proposal: using a single laser scanner, using three laser scanners and another with all the six laser scanners available in the dataset.

\subsection{Scene 1: Single laser scanner}

For this configuration laser scanner LMS2 is chosen because it has a good coverage of intersection and leg 2.

\subsection{Scene 2: Three laser scanners}

In this configuration selected laser scanners are LMS1, LMS2 and LMS3 trying to have a general coverage of the intersection from different views

\subsection{Scene 3: Six laser scanners}
This configuration uses all the available laser from the dataset.
